Estimating initial state and quark-gluon plasma medium properties \\ using a hybrid model with nucleon substructure \\ calibrated to $\boldsymbol p$-Pb and Pb-Pb collisions at \texorpdfstring{$\mathbf{\sqrts=5.02}$}{}~TeV

### 2018-08-10 paper/substructure.tex
Fix some of the bibtex entries.

\title{
  Estimating initial state and quark-gluon plasma medium properties \\
  using a hybrid model with nucleon substructure \\
  calibrated to p-Pb and Pb-Pb collisions at \texorpdfstring{$\mathbf{\sqrts=5.02}$}{}~TeV
}

@@

Hydrodynamic models of ultrarelativistic nuclear collisions are complicated by a number of theoretical unknowns, including the detailed geometry of the QGP initial conditions, the strength and duration of pre-equilibrium dynamics, the temperature dependence of QGP transport coefficients, and the boundaries of hydrodynamic applicability \cite{Niemi:2014lha, deSouza:2015ena, Ollitrault:2012cm, Song:2012ua}.
In general, these theoretical uncertainties tend to grow with decreasing system size, where emergent physics at sub-fermi length scales becomes important to describe bulk properties of the produced system.

>>>>

\title{
  Estimating initial state and quark-gluon plasma medium properties \\
  using a hybrid model with nucleon substructure \\
  calibrated to $\boldsymbol p$-Pb and Pb-Pb collisions at \texorpdfstring{$\mathbf{\sqrts=5.02}$}{}~TeV
}

@@

Hydrodynamic models of ultrarelativistic nuclear collisions are complicated by a number of theoretical unknowns, including the detailed geometry of the QGP initial conditions, the strength and duration of pre-equilibrium dynamics, the temperature dependence of QGP transport coefficients, and the boundaries of hydrodynamic applicability \cite{Niemi:2014lha, deSouza:2015ena, Ollitrault:2012cm, Song:2012ua}.
In general, these theoretical uncertainties tend to grow with decreasing system size, where emergent physics at sub-femtometer length scales becomes important to describe bulk properties of the produced system.
